---
title: "p8105_hw1_kq2127"
author: "Kristal Quispe"
date: "9/17/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Problem 1
```{r df_create and means}
p1_df = tibble(
  sample = rnorm(8),
  gr_th_0 = sample > 0, 
  vec_char = c("My", "complete", "full", "name", "is", "Jane", "Reed", "Doe"),
  vec_factor = factor(c("Green", "Red", "Red", "Blue", "Green", "Green", "Blue", "Blue"))
)


mean(pull(p1_df, sample))

mean(pull(p1_df, gr_th_0))

mean(pull(p1_df, vec_char))

mean(pull(p1_df, vec_factor))
```

When I take the mean of the first two variables in my data frame I get a result. The mean variable sample is `r mean(pull(p1_df, sample))` and the mean of variable gr_th_0 is `r mean(pull(p1_df, gr_th_0))` . I was not able to take the mean of the last two variables, vec_char and vec_factor because these two variables are not numeric or logical. 

```{r converting variables, eval = FALSE}
as.numeric(pull(p1_df, gr_th_0))

as.numeric(pull(p1_df, vec_char))

as.numeric(pull(p1_df, vec_factor))

```
When I convert the logical, character, and factor variables, only the logical variable is converted into 0s and 1s. The character variable is converted into NAs and the factor variable is converted into ... . This explains why we were able to take the mean of the logical variable, but not the mean of the character or factor variables. We can take a mean of a variable with numeric values of 0s and 1s, but not of NAs. 

```{r}
gr_th_0_num = as.numeric(pull(p1_df, gr_th_0))

gr_th_0_num*(pull(p1_df, sample))



gr_th_0_fac = as.factor(pull(p1_df, gr_th_0))

gr_th_0_fac*(pull(p1_df, sample))



gr_th_0_fac_num = as.numeric(as.factor(pull(p1_df, gr_th_0)))

gr_th_0_fac_num*(pull(p1_df, sample))
```

# Problem 2

```{r}
p2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  gr_th_1 = x + y > 1,
  num_vec = as.numeric(gr_th_1), 
  fac_vec = as.factor(gr_th_1)
)

```
The size of the dataset is `r nrow(p2_df)` rows and `r ncol(p2_df)` columns. The mean of x is `r mean(pull(p2_df, x))`, the median is `r median(pull(p2_df, x))`, and the standard deviation of x is `r sd(pull(p2_df, x))`. The proportion of cases for which x + y > 1 is


```{r yx_scatter}
xy_plot_l = ggplot(p2_df, aes(x = x, y = y, color = gr_th_1)) + geom_point()

xy_plot_l


xy_plot_n = ggplot(p2_df, aes(x = x, y = y, color = num_vec)) + geom_point()

xy_plot_n


xy_plot_f = ggplot(p2_df, aes(x = x, y = y, color = fac_vec)) + geom_point()

xy_plot_f


ggsave("xy_plot.png")

```
```
The color scale of the xy plot colored by the logical vector demonstrates 